\chapter{Introduction}
%\chapter{Einleitung}
\label{sec:introduction}

%general motivation for your work, context and goals: 1-2 pages
%
%\begin{itemize}
%\item \textbf{Context:} make sure to link where your work fits in
%\item \textbf{Problem:} gap in knowledge, too expensive, too slow, a deficiency, superseded technology
%\item \textbf{Strategy:} the way you will address the problem
%\end{itemize}

The characterization of nano-scaled materials becomes more and more important these days. This is due to the increasing interest of research in these materials and the downscaling of components in various fields of industries. %also quantum effects...
The \ac{APT} is an analysis technique that is able to resolve a material's structure on the atomic scale. 
It combines the methods \ac{FIM} and \ac{TOFMS}.%not really. Even though the techniques are related, FIM and AP are physically different.
A sharp tip, connected as positive electrode, is atom-by-atom stripped? by the process of field evaporation. This effect is achieved by applying a high electric field to the material causing \emph{quantum tunneling} of the ionized atoms on the surface.%That's not how field ionisation works....
A negatively biased counter electrode accelerates the field evaporated ions on a two dimensional position detector. The species of each atom can be determined by measuring its time of flight. Thus it is possible to assign the detected positions to both a layer of the material and its element species. The third dimension can be reconstructed by subsequently compose the detected layers \cite{Hel02}. %the original paper is from Bas et al. 1995 \\

The spatial reconstruction of the measured data can be used to visualize the result in three dimensions in order to get further understanding of the experimental outcome.